### 2021-05-05 article/article.tex
update

 \begin{figure}[!tb]
    \begin{center}
       \includegraphics[width=0.4\linewidth]{figures/DC_emm.pdf}
       \includegraphics[width=0.4\linewidth]{figures/DC_emt.pdf}
    \end{center}
    \caption{The expected values of $\Delta \chi^2$ after three years of PINGU data. $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
    parameters are set to zero. The black lines show the 90\% credibility region from~\cite{demidov}}\label{fig:DC_3D_et}
 \end{figure}

@@

>>>>

 \begin{figure}[!tb]
    \begin{center}
      \includegraphics[width=0.6\linewidth]{figures/DC_3D_NO.pdf}
      %\includegraphics[width=0.4\linewidth]{figures/DC_emm.pdf}
      %\includegraphics[width=0.4\linewidth]{figures/DC_emt.pdf}
    \end{center}
    \caption{The expected values of $\Delta \chi^2$ after three years of DC data. $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
    parameters other than the one displayed in each panel are set to zero. The black lines show the 90\% credibility region from~\cite{demidov}}\label{fig:DC_3D}
 \end{figure}

@@

\begin{table}
   \begin{center}
   \begin{tabular}{lcccc}
           \hline \hline && \multicolumn{3}{c} {\text {Best fit}} \\
           \cline { 3 - 5 } Parameter & 90\% CL & $\dm$ & $\theta_{23}$  & $\epsilon$  \\
           \hline
           $\ett$ & -0.028, 0.044 & 2.435 & 47.84 & 0.0125 \\
           $\emt$ & -0.015, 0.0050 & 2.435 & 43.97 & -0.005 \\
           $\eem$ & -0.068, 0.070 & 2.435 & 43.97 & 0 \\
           $\eet$ & -0.072, 0.14 & 2.435 & 43.97  & 0.05 \\
           \hline
       \label{table:DC_results}
   \end{tabular}
   \end{center}
   \caption{DeepCore results. Best fit points for $\dm$ and $\theta_{23}$ are given in units of $\si{10^{-3}\eV\squared}$ and
   $\si{\degree}$, respectively.}
\end{table}

\begin{table}
   \begin{center}
      \begin{tabular}{lcccc}
         \hline \hline && \multicolumn{3}{c} {\text {Best fit}} \\
         \cline { 3 - 5 } Parameter & 90\% CL & $\dm$ & $\theta_{23}$  & $\epsilon$  \\
         \hline
         $\ett$ &-& - & - & -\\
         $\emt$ &-& - & - & -\\
         $\eem$ & -0.060, 0.055 & 2.517 & 49.2 & 0 \\
         $\eet$ & -0.065, 0.072 & 2.517 & 49.2 & 0 \\
         \hline
      \label{table:PINGU_results}
      \end{tabular}
   \end{center}
   \caption{PINGU results. Best fit points for $\dm$ and $\theta_{23}$ are given in units of $\si{10^{-3}\eV\squared}$ and
   $\si{\degree}$, respectively.}
\end{table}

\begin{table}
   \begin{center}
   \begin{tabular}{lcccc}
           \hline \hline && \multicolumn{3}{c} {\text {Best fit}} \\
           \cline { 3 - 5 } Parameter & 90\% CL & $\dm$ & $\theta_{23}$  & $\epsilon$  \\
           \hline
           $\ett$ &-& - & - & -\\
           $\emt$ &-& - & - & -\\
           $\eem$ & -0.046, 0.046 \hspace{1cm}& 2.489 & 47.84 & 0 \\
           $\eet$ & -0.057, 0.028 \hspace{1cm}& 2.489 & 47.84 & 0 \\
           \hline
       \label{table:PINGU_results}
   \end{tabular}
   \end{center}
   \caption{Joint results. Best fit points for $\dm$ and $\theta_{23}$ are given in units of $\si{10^{-3}\eV\squared}$ and
   $\si{\degree}$, respectively.}
\end{table}
